Stochastic Approximation Monte Carlo with a Dynamic Update Factor (SAD)

### 2019-02-07 papers/histogram/sad.tex

>>>>

\subsection{$1/t$ Wang-Landau}
The Wang-Landau algorithm's error saturation can be corrected by
modifying the update factor such that it does not decrease too quickly.
Belardinelli and Pereyra raised the question as to whether the update
factor should be decrease by $\nicefrac12$ or some other factor for
each update~\cite{belardinelli2007fast}. They implemented a schedule
that enforced if the update factor $\gamma$ is less than
$\nicefrac{N_S}{t}$ then the update factor is set to
$\nicefrac{N_S}{t}$ and the histogram is no longer tracked. Employing
this scheduler, they found that the error saturation is avoided since
the correct density of states is approached asymptotically as
$t^{-\frac12}$~\cite{belardinelli2008analysis}. Zhou et. al further
confirmed that the WL algorithm never converges exponentially and
succesfully bounded the statistical error between
$t^{-\frac12}$ and $\nicefrac{1}{t}$~\cite{zhou2008optimal}.

Schneider et. al outlines minor refinements to the $1/t$ WL algorithm
including $\nicefrac{N_E}{t}$ scaling and switching from standard WL to
$1/t$ WL when the update factor $\gamma <
\nicefrac{N_E}{t}$~\cite{schneider2017convergence}. As per the original
$1/t$ implementation~\cite{belardinelli2007fast}, all energy states $N_E$
are required to be visited at least once $H(E) \neq 0$ effectively
avoiding the concept of `flatness'.
